---
title: "Monte Carlo simulations of infection prevention and control data analysed using structural equation models v3"
author: "Oliver Pearse"
date: "14/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r start, echo = FALSE, warning = FALSE, message = FALSE}

#downloading packages
library(tidyverse)
library(lavaan)
library(mvtnorm)
library(here)
library(gt)
library(ggdag)
library(generics)

#this simulation simulates a simple situation, focussing on environmental cleanliness
#it also allows to edit the effects of each layer on the next
sim_enveffect <- function(x, size = 52, baseline = 0.2, change_fid = 0.1, change_micro = 0.5, sepsis_baseline = 0.5, change_sepsis = 0.01){
  # this function simulates hand hygiene using multivariate normal dist
  mv_2 <- function(x, y, sigma = sigma_2, mv_scale = change_micro, ...){
    mv_scale <- 15 * mv_scale
    param <- rmvnorm(n = 1, mean = c(15 - x * mv_scale, 15 - y * mv_scale), sigma = sigma_2) 
    #param <- round(param)
    return(param)
  }
  
  #covariance matrix
  sigma_2 <- matrix(c(1, 0.5, 
                      0.5, 1), ncol = 2)
  
  #this function simulates environmental hygiene using multivariates normal dist
  mv_3 <- function(x, y, z, sigma = sigma_3, mv_scale = change_micro, ...){
    mv_scale <- 15 * mv_scale
    param <- rmvnorm(n = 1, mean = c(15 - x * mv_scale, 15 - y * mv_scale, 
                                     15 - z * mv_scale), sigma = sigma_3)
    #param <- round(param)
    return(param)
  }
  
  #covariance matrix
    sigma_3 <- matrix(c(1, 0.5, 0.5, 
                        0.5, 1, 0.5, 
                        0.5, 0.5, 1), ncol = 3)
  
  #simulating time
  weeks <- seq(1:size)
  #simulating interventions
  #hands
  int_h1 <- c(rep(0, round(size / 4)), rep(1, size - round(size / 4)))
  int_h2 <- c(rep(0, size - round(size / 3)), rep(1, round(size / 3)))
  int_h3 <- c(rep(0, round(size / 4 * 3)), rep(1, size - round(size / 4 * 3)))
  alpha_hands <- ((int_h1 + int_h2 + int_h3) * change_fid + baseline) * 10
  alpha_hands[alpha_hands<0] <- 0
  alpha_hands[alpha_hands>10] <- 10
  beta_hands <- 10 - alpha_hands
  #environment
  int_e1 <- c(rep(0, round(size / 3)), rep(1, size - round(size / 3)))
  int_e2 <- c(rep(0, round(size / 2)), rep(1, size - round(size / 2)))
  int_e3 <- c(rep(0, round(size / 10 * 2)), rep(1, size - round(size / 10 * 2)))
  alpha_env <- ((int_e1 + int_e2 + int_e3) * change_fid + baseline) * 10
  alpha_env[alpha_env<0] <- 0
  alpha_env[alpha_env>10] <- 10
  beta_env <- 10 - alpha_env

  #simulating fidelity of intervention
  #overall environmental
  fid_cot <- rbeta(size, alpha_env, beta_env)
  fid_floor <- rbeta(size, alpha_env, beta_env)
  fid_surf <- rbeta(size, alpha_env, beta_env)
  #hands
  fid_mat <- rbeta(size, alpha_hands, beta_hands)
  fid_staff <- rbeta(size, alpha_hands, beta_hands)
  #microbiology
  #environmental
  mv_env <- mapply(FUN = mv_3, x = fid_cot, y = fid_floor, 
                   z = fid_surf, MoreArgs = list(sigma = sigma_3, mv_scale = change_micro))
  micro_cot <- mv_env[1, ]
  micro_floor <- mv_env[2, ]
  micro_surf <- mv_env[3, ]

  #hands
  mv_hands <- mapply(FUN = mv_2, x = fid_staff, y = fid_mat, 
                     MoreArgs = list(sigma = sigma_2, mv_scale = change_micro))
  micro_staff <- mv_hands[1, ]
  micro_mat <- mv_hands[2, ]
  #sepsis
  #this allows sepsis to be scaled and a baseline decided upon
  all_micro <- micro_cot + micro_floor + micro_surf + micro_staff + micro_mat
  max_micro <- max(all_micro)
  #baseline alpha
  alpha0 <- sepsis_baseline * 100
  #baseline beta
  beta0 <- 100 - alpha0
  #change in micro relative to baseline
  microD <- max_micro - all_micro
  #delta
  delta <- change_sepsis * microD
  #alpha to use
  alpha_sepsis <- alpha0 - (alpha0 + beta0) * delta
  alpha_sepsis[alpha_sepsis < 0] <- 0
  #beta to use
  beta_sepsis <- beta0 + (alpha0 + beta0) * delta
  beta_sepsis[beta_sepsis < 0] <- 0
  alpha_sepsis[(alpha_sepsis / (alpha_sepsis + beta_sepsis)) < 0.02] <- 2
  #sepsis
  sepsis <- rbeta(size, alpha_sepsis, beta_sepsis)
  
  #creating data frame
  df_ipc <- data.frame(
    weeks = weeks,
    int_e1 = int_e1,
    int_e2 = int_e2,
    int_e3 = int_e3,
    int_h1 = int_h1,
    int_h2 = int_h2,
    int_h3 = int_h3,
    fid_cot = fid_cot,
    fid_floor = fid_floor,
    fid_surf = fid_surf,
    fid_mat = fid_mat,
    fid_staff = fid_staff,
    micro_cot = micro_cot,
    micro_floor = micro_floor,
    micro_surf = micro_surf,
    micro_staff = micro_staff,
    micro_mat = micro_mat,
    sepsis = sepsis
  )
  return(df_ipc)
}

#this simulation simulates a simple situation, focussing on environmental cleanliness
#it also allows to edit the effects of each layer on the next
sim_envindiv <- function(x, size = 52, baseline = 0.2, change_fid = 0.1, change_micro = 0.5, sepsis_baseline = 0.5, change_sepsis = 0.01, 
                         e1_mult = 1, e2_mult = 1, e3_mult = 1, cot_mult = 1, surf_mult = 1, floor_mult = 1, staff_mult = 1, mat_mult = 1){
  # this function simulates hand hygiene using multivariate normal dist
  mv_2 <- function(x, y, sigma = sigma_2, mv_scale = change_micro, ...){
    mv_scale <- 15 * mv_scale
    param <- rmvnorm(n = 1, mean = c(15 - x * mv_scale, 15 - y * mv_scale), sigma = sigma_2) 
    #param <- round(param)
    return(param)
  }
  
  #covariance matrix
  sigma_2 <- matrix(c(1, 0.5, 
                      0.5, 1), ncol = 2)
  
  #this function simulates environmental hygiene using multivariates normal dist
  mv_3 <- function(x, y, z, sigma = sigma_3, mv_scale = change_micro, ...){
    mv_scale <- 15 * mv_scale
    param <- rmvnorm(n = 1, mean = c(15 - x * mv_scale, 15 - y * mv_scale, 
                                     15 - z * mv_scale), sigma = sigma_3)
    #param <- round(param)
    return(param)
  }
  
  #covariance matrix
    sigma_3 <- matrix(c(1, 0.5, 0.5, 
                        0.5, 1, 0.5, 
                        0.5, 0.5, 1), ncol = 3)
  
  #simulating time
  weeks <- seq(1:size)
  #simulating interventions
  #hands
  int_h1 <- c(rep(0, round(size / 4)), rep(1, size - round(size / 4)))
  int_h2 <- c(rep(0, size - round(size / 3)), rep(1, round(size / 3)))
  int_h3 <- c(rep(0, round(size / 4 * 3)), rep(1, size - round(size / 4 * 3)))
  alpha_hands <- ((int_h1 + int_h2 + int_h3) * change_fid + baseline) * 10
  alpha_hands[alpha_hands<0] <- 0
  alpha_hands[alpha_hands>10] <- 10
  beta_hands <- 10 - alpha_hands
  #environment
  int_e1 <- c(rep(0, round(size / 3)), rep(1, size - round(size / 3)))
  int_e2 <- c(rep(0, round(size / 2)), rep(1, size - round(size / 2)))
  int_e3 <- c(rep(0, round(size / 10 * 2)), rep(1, size - round(size / 10 * 2)))
  alpha_env <- ((int_e1 * e1_mult + int_e2 * e2_mult + int_e3 * e3_mult) * change_fid + baseline) * 10
  alpha_env[alpha_env<0] <- 0
  alpha_env[alpha_env>10] <- 10
  beta_env <- 10 - alpha_env

  #simulating fidelity of intervention
  #overall environmental
  fid_cot <- rbeta(size, alpha_env, beta_env)
  fid_floor <- rbeta(size, alpha_env, beta_env)
  fid_surf <- rbeta(size, alpha_env, beta_env)
  #hands
  fid_mat <- rbeta(size, alpha_hands, beta_hands)
  fid_staff <- rbeta(size, alpha_hands, beta_hands)
  #microbiology
  #environmental
  mv_env <- mapply(FUN = mv_3, x = fid_cot, y = fid_floor, 
                   z = fid_surf, MoreArgs = list(sigma = sigma_3, mv_scale = change_micro))
  micro_cot <- mv_env[1, ]
  micro_floor <- mv_env[2, ]
  micro_surf <- mv_env[3, ]

  #hands
  mv_hands <- mapply(FUN = mv_2, x = fid_staff, y = fid_mat, 
                     MoreArgs = list(sigma = sigma_2, mv_scale = change_micro))
  micro_staff <- mv_hands[1, ]
  micro_mat <- mv_hands[2, ]
  #sepsis
  #this allows sepsis to be scaled and a baseline decided upon
  all_micro <- micro_cot * cot_mult + micro_floor * floor_mult + micro_surf * surf_mult + micro_staff * staff_mult + micro_mat * mat_mult
  max_micro <- max(all_micro)
  #baseline alpha
  alpha0 <- sepsis_baseline * 100
  #baseline beta
  beta0 <- 100 - alpha0
  #change in micro relative to baseline
  microD <- max_micro - all_micro
  #delta
  delta <- change_sepsis * microD
  #alpha to use
  alpha_sepsis <- alpha0 - (alpha0 + beta0) * delta
  alpha_sepsis[alpha_sepsis < 0] <- 0
  #beta to use
  beta_sepsis <- beta0 + (alpha0 + beta0) * delta
  beta_sepsis[beta_sepsis < 0] <- 0
  alpha_sepsis[(alpha_sepsis / (alpha_sepsis + beta_sepsis)) < 0.02] <- 2
  #sepsis
  sepsis <- rbeta(size, alpha_sepsis, beta_sepsis)
  #number of patients on the ward
  pats <- rpois(size, 100)
  #number of sepsis cases
  cases <- rbinom(size, pats, sepsis)
  
  #creating data frame
  df_ipc <- data.frame(
    weeks = weeks,
    int_e1 = int_e1,
    int_e2 = int_e2,
    int_e3 = int_e3,
    int_h1 = int_h1,
    int_h2 = int_h2,
    int_h3 = int_h3,
    fid_cot = fid_cot,
    fid_floor = fid_floor,
    fid_surf = fid_surf,
    fid_mat = fid_mat,
    fid_staff = fid_staff,
    micro_cot = micro_cot,
    micro_floor = micro_floor,
    micro_surf = micro_surf,
    micro_staff = micro_staff,
    micro_mat = micro_mat,
    sepsis = sepsis,
    pats = pats,
    cases = cases
  )
  
  all_data <- data.frame()
  for (i in weeks){
    pats <- df_ipc[i, "pats"]
    cases <- df_ipc[i, "cases"]
    outcome <- c(rep(1, cases), rep(0, pats - cases))
    cov <- df_ipc[i, ]
    cov <- cov %>% slice(rep(1:n(), each = pats))
    data <- cbind(cov, outcome)
    all_data <- rbind(all_data, data)
  }
  return(all_data)
}


#this function repeats the simulation a certain number of times and then plots it
sim_timeseries <- function(func = func, reps = 100, size = 52, baseline = 0.2, change_fid = 0.1, change_micro = 0.5, change_sepsis = 0.01, sepsis_baseline = 0.5){
  fidcot_all <- data.frame()
  fidfloor_all <- data.frame()
  fidsurf_all <- data.frame()
  fidmat_all <- data.frame()
  fidstaff_all <- data.frame()
  microcot_all <- data.frame()
  microfloor_all <- data.frame()
  microsurf_all <- data.frame()
  micromat_all <- data.frame()
  microstaff_all <- data.frame()
  sepsis_all <- data.frame()
  for(i in 1:reps){
    #simulating time
    data_run <- func(x = i, size = size, baseline = baseline, change_fid = change_fid, 
                   change_micro = change_micro, change_sepsis = change_sepsis, sepsis_baseline = sepsis_baseline)

    fidcot_all <- rbind(fidcot_all, data_run$fid_cot)
    fidfloor_all <- rbind(fidfloor_all, data_run$fid_floor)
    fidsurf_all <- rbind(fidsurf_all, data_run$fid_surf)
    fidmat_all <- rbind(fidmat_all, data_run$fid_mat)
    fidstaff_all <- rbind(fidstaff_all, data_run$fid_staff)
    microcot_all <- rbind(microcot_all, data_run$micro_cot)
    microfloor_all <- rbind(microfloor_all, data_run$micro_floor)
    microsurf_all <- rbind(microsurf_all, data_run$micro_surf)
    micromat_all <- rbind(micromat_all, data_run$micro_mat)
    microstaff_all <- rbind(microstaff_all, data_run$micro_staff)
    sepsis_all <- rbind(sepsis_all, data_run$sepsis)
  }
fidcot_stats <- sapply(fidcot_all, FUN = quantile)
fidcot_stats2 <- as.data.frame(t(fidcot_stats))
microcot_stats <- sapply(microcot_all, FUN = quantile)
microcot_stats2 <- as.data.frame(t(microcot_stats)) / 15
sepsis_stats <- sapply(sepsis_all, FUN = quantile)
sepsis_stats2 <- as.data.frame(t(sepsis_stats))
interventions <- c(Position(function(x) x > 0, data_run$int_h1),
                   Position(function(x) x > 0, data_run$int_h2),
                   Position(function(x) x > 0, data_run$int_h3),
                   Position(function(x) x > 0, data_run$int_e1),
                   Position(function(x) x > 0, data_run$int_e2),
                   Position(function(x) x > 0, data_run$int_e3))

colors <- c("fidcot_stats2" = "black", "microcot_stats2" = "blue", "sepsis_stats2" = "red")
ggplot() + 
  geom_line(data = fidcot_stats2, aes(y = `50%`, x = seq(1:52)), colour = "black") + 
  geom_ribbon(data = fidcot_stats2, aes(ymin = `25%`, ymax = `75%`, x = seq(1:52)), alpha = 0.5, fill = "black") + 
  geom_line(data = microcot_stats2, aes(y = `50%`, x = seq(1:52)), colour = "blue") + 
  geom_ribbon(data = microcot_stats2, aes(ymin = `25%`, ymax = `75%`, x = seq(1:52)), alpha = 0.5, fill = "blue") +
  geom_line(data = sepsis_stats2, aes(y = `50%`, x = seq(1:52)), colour = "red") + 
  geom_ribbon(data = sepsis_stats2, aes(ymin = `25%`, ymax = `75%`, x = seq(1:52)), alpha = 0.5, fill = "red") +
  geom_vline(xintercept = interventions) +
  scale_y_continuous(name = "Proportion fidelity of cleanliness and neonates with sepsis", limits = c(0, 1),
                     sec.axis = sec_axis(trans=~.*15, name = "Microbiology")) +
  labs(color = "Legend") +
  xlab("Week of study") +
  scale_color_manual(values = colors)
}
  
sem_env <- function(func, size = 52, baseline = 0.2, change_fid = 0.1, change_micro = 0.5, sepsis_baseline = 0.5, change_sepsis = 0.01, x = 1){ 
  df_ipc <- func(size = size, baseline = baseline, change_fid = change_fid, change_micro = change_micro, 
                 sepsis_baseline = sepsis_baseline, change_sepsis = change_sepsis, x = x)
  df2 <- as.data.frame(apply(df_ipc, 2, scale))
  
  #first model ----
  #lavaan formulation without latent variables
  ipc_model <- '
    #regressions
    fid_cot ~ int_e1 + int_e2 + int_e3
    fid_floor ~ int_e1 + int_e2 + int_e3
    fid_surf ~ int_e1 + int_e2 + int_e3
    
    micro_cot ~ fid_cot
    micro_floor ~ fid_floor
    micro_surf ~ fid_surf

    sepsis ~ micro_cot + micro_floor + micro_surf + micro_mat + micro_staff
    
    #covariance
    micro_cot ~~ micro_floor
    micro_cot ~~ micro_surf
    micro_floor ~~ micro_surf
  '
  
  #fitting the model
  ipc_fit <- sem(ipc_model, data = df2)
  
  #finding the effect size
  effect <- glm(sepsis ~ int_e1 + int_e2 + int_e3 + int_h1 + int_h2 + int_h3, data = df2)
  
  #getting the parameter estimates
  params <- try(parameterEstimates(ipc_fit), silent = TRUE) %>%
    filter(op == "~") %>%
    unite(param, c("lhs", "op", "rhs"), remove = FALSE) %>%
    dplyr::select(param, est)
  
  #converting them to the right orientation
  params2 <- t(params$est)
  colnames(params2) <- params$param
  
  #determining whether the simulation would pass the decision rule
  pass <- case_when(isTRUE((try(fitMeasures(ipc_fit), silent = TRUE)["pvalue"] >= 0.05) &
                    (try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"] <= 0.05 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["srmr"] <= 0.1) |
                    (try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"] <= 0.1 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["srmr"] <= 0.05) &
                    (try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"] >= 0.97 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["cfi"] >= 0.90) |
                    (try(fitMeasures(ipc_fit), silent = TRUE)["cfi"] >= 0.97 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"] >= 0.90))
                      ~ "Good",
                    isTRUE((try(fitMeasures(ipc_fit), silent = TRUE)["pvalue"] >= 0.01) &
                    (try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"] <= 0.08 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["srmr"] <= 0.1) |
                    (try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"] <= 0.1 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["srmr"] <= 0.08) &
                    (try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"] >= 0.95 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["cfi"] >= 0.90) |
                    (try(fitMeasures(ipc_fit), silent = TRUE)["cfi"] >= 0.95 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"] >= 0.90))
                    ~ "Acceptable",
                    TRUE ~ "Poor")
  
  #extracting data from the model
  data <- cbind(data.frame(run = x,
                           chisq = try(fitMeasures(ipc_fit), silent = TRUE)["chisq"],
                           df = try(fitMeasures(ipc_fit), silent = TRUE)["df"],
                           pvalue = try(fitMeasures(ipc_fit), silent = TRUE)["pvalue"],
                           rmsea = try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"], 
                           rmsea.ci.lower = try(fitMeasures(ipc_fit), silent = TRUE)["rmsea.ci.lower"],
                           rmsea.ci.upper = try(fitMeasures(ipc_fit), silent = TRUE)["rmsea.ci.upper"],
                           rmsea.pvalue = try(fitMeasures(ipc_fit), silent = TRUE)["rmsea.pvalue"],
                           srmr = try(fitMeasures(ipc_fit), silent = TRUE)["srmr"],
                           nnfi = try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"],
                           cfi = try(fitMeasures(ipc_fit), silent = TRUE)["cfi"],
                           aic = try(fitMeasures(ipc_fit), silent = TRUE)["aic"],
                           gfi = try(fitMeasures(ipc_fit), silent = TRUE)["gfi"],
                           agfi = try(fitMeasures(ipc_fit), silent = TRUE)["agfi"],
                           pass = pass,
                           params2,
                           effect1 = effect$coefficients[2],
                           effect2 = effect$coefficients[3],
                           effect3 = effect$coefficients[4],
                           effectall = mean(c(effect$coefficients[2], effect$coefficients[3], effect$coefficients[4])),
                           change_fid = change_fid,
                           change_micro = change_micro,
                           change_sepsis = change_sepsis
  ))
  rownames(data) <- c()
  return(data)
}

sem_env_intonly <- function(func, size = 52, baseline = 0.2, change_fid = 0.1, change_micro = 0.5, sepsis_baseline = 0.5, change_sepsis = 0.01, x = 1){ 
  df_ipc <- func(size = size, baseline = baseline, change_fid = change_fid, change_micro = change_micro, 
                 sepsis_baseline = sepsis_baseline, change_sepsis = change_sepsis, x = x)
  df2 <- as.data.frame(apply(df_ipc, 2, scale))
  
  #first model ----
  #lavaan formulation without latent variables
  ipc_model <- '
    #regressions
    sepsis ~ int_e1 + int_e2 + int_e3
    
  '
  
  #fitting the model
  ipc_fit <- sem(ipc_model, data = df2)
  
  #finding the effect size
  effect <- glm(sepsis ~ int_e1 + int_e2 + int_e3 + int_h1 + int_h2 + int_h3, data = df2)
  
  #getting the parameter estimates
  params <- try(parameterEstimates(ipc_fit), silent = TRUE) %>%
    filter(op == "~") %>%
    unite(param, c("lhs", "op", "rhs"), remove = FALSE) %>%
    dplyr::select(param, est)
  
  #converting them to the right orientation
  params2 <- t(params$est)
  colnames(params2) <- params$param
  
  #determining whether the simulation would pass the decision rule
  pass <- case_when(isTRUE((try(fitMeasures(ipc_fit), silent = TRUE)["pvalue"] >= 0.05) &
                    (try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"] <= 0.05 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["srmr"] <= 0.1) |
                    (try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"] <= 0.1 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["srmr"] <= 0.05) &
                    (try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"] >= 0.97 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["cfi"] >= 0.90) |
                    (try(fitMeasures(ipc_fit), silent = TRUE)["cfi"] >= 0.97 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"] >= 0.90))
                      ~ "Good",
                    isTRUE((try(fitMeasures(ipc_fit), silent = TRUE)["pvalue"] >= 0.01) &
                    (try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"] <= 0.08 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["srmr"] <= 0.1) |
                    (try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"] <= 0.1 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["srmr"] <= 0.08) &
                    (try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"] >= 0.95 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["cfi"] >= 0.90) |
                    (try(fitMeasures(ipc_fit), silent = TRUE)["cfi"] >= 0.95 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"] >= 0.90))
                    ~ "Acceptable",
                    TRUE ~ "Poor")
  
  #extracting data from the model
  data <- cbind(data.frame(run = x,
                           chisq = try(fitMeasures(ipc_fit), silent = TRUE)["chisq"],
                           df = try(fitMeasures(ipc_fit), silent = TRUE)["df"],
                           pvalue = try(fitMeasures(ipc_fit), silent = TRUE)["pvalue"],
                           rmsea = try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"], 
                           rmsea.ci.lower = try(fitMeasures(ipc_fit), silent = TRUE)["rmsea.ci.lower"],
                           rmsea.ci.upper = try(fitMeasures(ipc_fit), silent = TRUE)["rmsea.ci.upper"],
                           rmsea.pvalue = try(fitMeasures(ipc_fit), silent = TRUE)["rmsea.pvalue"],
                           srmr = try(fitMeasures(ipc_fit), silent = TRUE)["srmr"],
                           nnfi = try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"],
                           cfi = try(fitMeasures(ipc_fit), silent = TRUE)["cfi"],
                           aic = try(fitMeasures(ipc_fit), silent = TRUE)["aic"],
                           gfi = try(fitMeasures(ipc_fit), silent = TRUE)["gfi"],
                           agfi = try(fitMeasures(ipc_fit), silent = TRUE)["agfi"],
                           pass = pass,
                           params2,
                           effect1 = effect$coefficients[2],
                           effect2 = effect$coefficients[3],
                           effect3 = effect$coefficients[4],
                           effectall = mean(c(effect$coefficients[2], effect$coefficients[3], effect$coefficients[4])),
                           change_fid = change_fid,
                           change_micro = change_micro,
                           change_sepsis = change_sepsis
  ))
  rownames(data) <- c()
  return(data)
}


sem_env_intfid <- function(func, size = 52, baseline = 0.2, change_fid = 0.1, change_micro = 0.5, sepsis_baseline = 0.5, change_sepsis = 0.01, x = 1){ 
  df_ipc <- func(size = size, baseline = baseline, change_fid = change_fid, change_micro = change_micro, 
                 sepsis_baseline = sepsis_baseline, change_sepsis = change_sepsis, x = x)
  df2 <- as.data.frame(apply(df_ipc, 2, scale))
  
  #first model ----
  #lavaan formulation without latent variables
  ipc_model <- '
    #regressions
    fid_cot ~ int_e1 + int_e2 + int_e3
    fid_floor ~ int_e1 + int_e2 + int_e3
    fid_surf ~ int_e1 + int_e2 + int_e3

    
    sepsis ~ fid_cot + fid_floor + fid_surf
    
  '
  
  #fitting the model
  ipc_fit <- sem(ipc_model, data = df2)
  
  #finding the effect size
  effect <- glm(sepsis ~ int_e1 + int_e2 + int_e3 + int_h1 + int_h2 + int_h3, data = df2)
  
  #getting the parameter estimates
  params <- try(parameterEstimates(ipc_fit), silent = TRUE) %>%
    filter(op == "~") %>%
    unite(param, c("lhs", "op", "rhs"), remove = FALSE) %>%
    dplyr::select(param, est)
  
  #converting them to the right orientation
  params2 <- t(params$est)
  colnames(params2) <- params$param
  
  #determining whether the simulation would pass the decision rule
  pass <- case_when(isTRUE((try(fitMeasures(ipc_fit), silent = TRUE)["pvalue"] >= 0.05) &
                    (try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"] <= 0.05 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["srmr"] <= 0.1) |
                    (try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"] <= 0.1 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["srmr"] <= 0.05) &
                    (try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"] >= 0.97 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["cfi"] >= 0.90) |
                    (try(fitMeasures(ipc_fit), silent = TRUE)["cfi"] >= 0.97 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"] >= 0.90))
                      ~ "Good",
                    isTRUE((try(fitMeasures(ipc_fit), silent = TRUE)["pvalue"] >= 0.01) &
                    (try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"] <= 0.08 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["srmr"] <= 0.1) |
                    (try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"] <= 0.1 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["srmr"] <= 0.08) &
                    (try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"] >= 0.95 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["cfi"] >= 0.90) |
                    (try(fitMeasures(ipc_fit), silent = TRUE)["cfi"] >= 0.95 &
                    try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"] >= 0.90))
                    ~ "Acceptable",
                    TRUE ~ "Poor")
  
  #extracting data from the model
  data <- cbind(data.frame(run = x,
                           chisq = try(fitMeasures(ipc_fit), silent = TRUE)["chisq"],
                           df = try(fitMeasures(ipc_fit), silent = TRUE)["df"],
                           pvalue = try(fitMeasures(ipc_fit), silent = TRUE)["pvalue"],
                           rmsea = try(fitMeasures(ipc_fit), silent = TRUE)["rmsea"], 
                           rmsea.ci.lower = try(fitMeasures(ipc_fit), silent = TRUE)["rmsea.ci.lower"],
                           rmsea.ci.upper = try(fitMeasures(ipc_fit), silent = TRUE)["rmsea.ci.upper"],
                           rmsea.pvalue = try(fitMeasures(ipc_fit), silent = TRUE)["rmsea.pvalue"],
                           srmr = try(fitMeasures(ipc_fit), silent = TRUE)["srmr"],
                           nnfi = try(fitMeasures(ipc_fit), silent = TRUE)["nnfi"],
                           cfi = try(fitMeasures(ipc_fit), silent = TRUE)["cfi"],
                           aic = try(fitMeasures(ipc_fit), silent = TRUE)["aic"],
                           gfi = try(fitMeasures(ipc_fit), silent = TRUE)["gfi"],
                           agfi = try(fitMeasures(ipc_fit), silent = TRUE)["agfi"],
                           pass = pass,
                           params2,
                           effect1 = effect$coefficients[2],
                           effect2 = effect$coefficients[3],
                           effect3 = effect$coefficients[4],
                           effectall = mean(c(effect$coefficients[2], effect$coefficients[3], effect$coefficients[4])),
                           change_fid = change_fid,
                           change_micro = change_micro,
                           change_sepsis = change_sepsis
  ))
  rownames(data) <- c()
  return(data)
}

#this outputs the logbinomial model on simulated data
#the effects of the interventions can be edited
logbin_ipcsepsis <- function(func, reps = 100, size = 52, baseline = 0.2, change_fid = 0.1, change_micro = 0.5, sepsis_baseline = 0.5, change_sepsis = 0.01, 
                         e1_mult = 1, e2_mult = 1, e3_mult = 1, cot_mult = 1, surf_mult = 1, floor_mult = 1, staff_mult = 1, mat_mult = 1){
  all_data <- data.frame()
  for (i in 1:reps){
    run <- func(size = size, baseline = baseline, change_fid = change_fid, change_micro = change_micro, sepsis_baseline = sepsis_baseline, change_sepsis = change_sepsis, e1_mult = e1_mult, e2_mult = e2_mult, e3_mult = e3_mult, cot_mult = cot_mult, surf_mult = surf_mult, floor_mult = floor_mult, staff_mult = staff_mult, mat_mult = mat_mult)
    model <- glm(outcome ~ int_e1 + int_e2 + int_e3, data = run, family = binomial(link = "log"))# start=c(log(mean(outcome)), rep(0, 3)))
    inter1 <- exp(model$coefficients[2])
    inter2 <- exp(model$coefficients[3])
    inter3 <- exp(model$coefficients[4])
    converged <- model$converged
    data <- data.frame(run = i, int_e1 = inter1, int_e2 = inter2, int_e3 = inter3, converged)
    all_data <- rbind(all_data, data)
  }
  effects <- colMeans(all_data %>% select(starts_with("int"), converged))
  return(effects)
}

#this simulates data and outputs the linear regression model 
#the effects of the interventions can be edited
logbin_microsepsis <- function(func, reps = 100, size = 52, baseline = 0.2, change_fid = 0.1, change_micro = 0.5, sepsis_baseline = 0.5, change_sepsis = 0.01, 
                         e1_mult = 1, e2_mult = 1, e3_mult = 1, cot_mult = 1, surf_mult = 1, floor_mult = 1, staff_mult = 1, mat_mult = 1){
  all_data <- data.frame()
  for (i in 1:reps){
    run <- func(size = size, baseline = baseline, change_fid = change_fid, change_micro = change_micro, sepsis_baseline = sepsis_baseline, change_sepsis = change_sepsis, e1_mult = e1_mult, e2_mult = e2_mult, e3_mult = e3_mult, cot_mult = cot_mult, surf_mult = surf_mult, floor_mult = floor_mult, staff_mult = staff_mult, mat_mult = mat_mult)
    model <- glm(outcome ~ micro_cot + micro_surf + micro_floor + micro_mat + micro_staff, data = run, family = binomial(link = "log"))
    cot <- exp(model$coefficients[2])
    surf <- exp(model$coefficients[3])
    floor <- exp(model$coefficients[4])
    mat <- exp(model$coefficients[5])
    staff <- exp(model$coefficients[6])
    converged <- model$converged
    data <- data.frame(run = i, cot = cot, surf = surf, floor = floor, mat = mat, staff = staff, converged = converged)
    all_data <- rbind(all_data, data)
  }
  effects <- colMeans(all_data %>% select(-run))
  return(effects)
}

#this function repeats the simulation a certain number of times and then plots it
lin_microsepsis <- function(func = func, reps = 100, size = 52, baseline = 0.2, change_fid = 0.1, change_micro = 0.5, change_sepsis = 0.01, sepsis_baseline = 0.5){
  micro_all <- c()
  sepsis_all <- c()
  intercept_all <- c()
  slope_all <- c()
  for(i in 1:reps){
    #simulating time
    data_run <- func(x = i, size = size, baseline = baseline, change_fid = change_fid, 
                   change_micro = change_micro, change_sepsis = change_sepsis, sepsis_baseline = sepsis_baseline)
    micro <- (data_run$micro_cot + data_run$micro_floor + data_run$micro_surf + data_run$micro_staff + data_run$micro_mat) / 5
    sepsis <- data_run$sepsis
    model <- glm(sepsis ~ micro, data = data_run)
    intercept <- model$coefficients[1]
    slope <- model$coefficients[2]
    micro_all <- c(micro_all, micro)
    sepsis_all <- c(sepsis_all, sepsis)
    intercept_all <- c(intercept_all, intercept)
    slope_all <- c(slope_all, slope)
    dataind <- data.frame(micro = micro, sepsis = sepsis)
  }
  data <- data.frame(micro = micro_all, sepsis = sepsis_all)
  mean_slope <- mean(slope_all)
  mean_intercept <- mean(intercept_all)
  ggplot() +
    geom_point(data = dataind, aes(x = micro, y = sepsis), colour = "blue") +
    geom_abline(intercept = mean_intercept, slope = mean_slope, colour = "black", lwd = 2) +
    geom_abline(intercept = intercept_all, slope = slope_all, colour = "black", alpha = 0.05, lwd = 1) +
    ylim(0, 1) +
    xlab("Microbiology") +
    ylab("Proportion neonates with sepsis")
}

#this function runs the simulation function a certain number of times and collates the results
#it should be used for the functions which have the ability to change individual relationships
mult_sorting_effect <- function(func1, func2, reps = 100, size = 52, baseline = 0.2, change_fid = 0.1, change_sepsis = 0.01, sepsis_baseline = 0.5, change_micro = 0.5){
  sim_mult <- do.call("rbind", lapply(X = seq(1:reps), FUN = func1, 
                                      baseline = baseline, size = size, 
                                      change_fid = change_fid, change_sepsis = change_sepsis, 
                                      sepsis_baseline = sepsis_baseline, change_micro = change_micro,
                                      func = func2))
  sim_mult2 <- lapply(sim_mult, as.numeric)
  fit_mult <- data.frame(
    chisq = c(sum(sim_mult2$chisq < sapply(sim_mult2$df, FUN = prod ,2), na.rm = TRUE) / length(sim_mult2$chisq), 
              sum(sim_mult2$chisq < sapply(sim_mult2$df, FUN = prod ,3) , na.rm = TRUE) / length(sim_mult2$chisq)),
    pvalue = c(sum(sim_mult2$pvalue >= 0.05, na.rm = TRUE) / length(sim_mult2$pvalue), 
               sum(sim_mult2$pvalue >= 0.01, na.rm = TRUE) / length(sim_mult2$pvalue)),
    rmsea = c(sum(sim_mult2$rmsea <= 0.05, na.rm = TRUE) / length(sim_mult2$rmsea), 
              sum(sim_mult2$rmsea <= 0.08, na.rm = TRUE) / length(sim_mult2$rmsea)),
    rmsea.pvalue = c(sum(sim_mult2$rmsea.pvalue > 0.1, na.rm = TRUE) / length(sim_mult2$rmsea.pvalue), 
                     sum(sim_mult2$rmsea.pvalue > 0.05, na.rm = TRUE) / length(sim_mult2$rmsea.pvalue)),
    srmr = c(sum(sim_mult2$srmr <= 0.05, na.rm = TRUE) / length(sim_mult2$srmr), 
             sum(sim_mult2$srmr <= 0.1, na.rm = TRUE) / length(sim_mult2$srmr)),
    nnfi = c(sum(sim_mult2$nnfi >= 0.97, na.rm = TRUE) / length(sim_mult2$nnfi), 
             sum(sim_mult2$nnfi >= 0.95, na.rm = TRUE) / length(sim_mult2$nnfi)),
    cfi = c(sum(sim_mult2$cfi >= 0.97, na.rm = TRUE) / length(sim_mult2$cfi), 
            sum(sim_mult2$cfi >= 0.95, na.rm = TRUE) / length(sim_mult2$cfi)),
    aic = c(mean(sim_mult2$aic),
            mean(sim_mult2$aic)),
    gfi = c(mean(sim_mult2$gfi),
            mean(sim_mult2$gfi)),
    agfi = c(mean(sim_mult2$agfi),
             mean(sim_mult2$agfi)),
    effect = c(mean(sim_mult2$effectall),
               mean(sim_mult2$effectall)),
    good = sum(sim_mult$pass == "Good", na.rm = TRUE) / length(sim_mult$pass),
    acceptable = (sum(sim_mult$pass == "Acceptable", na.rm = TRUE) +  sum(sim_mult$pass == "Good", na.rm = TRUE)) / length(sim_mult$pass),
    change_fid = c(mean(sim_mult2$change_fid), mean(sim_mult2$change_fid)),
    change_micro = c(mean(sim_mult2$change_micro), mean(sim_mult2$change_micro)), 
    change_sepsis = c(mean(sim_mult2$change_sepsis), mean(sim_mult2$change_sepsis)),
    sample_size = c(size, size),
    effect1 = c(mean(sim_mult2$effect1),
                mean(sim_mult2$effect1)),
    effect2 = c(mean(sim_mult2$effect2),
                mean(sim_mult2$effect2)),
    effect3 = c(mean(sim_mult2$effect3),
                mean(sim_mult2$effect3))
    
  )
  rownames(fit_mult) <- c("good", "acceptable")
  return(fit_mult)
}

#this function runs the simulation function a certain number of times and collates the results
#it should be used for functions that do not have the ability to change individual relationships
mult_sorting <- function(func, reps = 100, size = 52, baseline = 0.2, change_fid = 0.1, sepsis_baseline = 0.5, change_micro = 1, change_sepsis = 0.01){
  sim_mult <- do.call("rbind", lapply(X = seq(1:reps), FUN = func, 
                                      baseline = baseline, size = size, 
                                      change_fid = change_fid))
  sim_mult2 <- lapply(sim_mult, as.numeric)
  fit_mult <- data.frame(
    chisq = c(sum(sim_mult2$chisq < sapply(sim_mult2$df, FUN = prod ,2), na.rm = TRUE) / length(sim_mult2$chisq), 
              sum(sim_mult2$chisq < sapply(sim_mult2$df, FUN = prod ,3) , na.rm = TRUE) / length(sim_mult2$chisq)),
    pvalue = c(sum(sim_mult2$pvalue >= 0.05, na.rm = TRUE) / length(sim_mult2$pvalue), 
               sum(sim_mult2$pvalue >= 0.01, na.rm = TRUE) / length(sim_mult2$pvalue)),
    rmsea = c(sum(sim_mult2$rmsea <= 0.05, na.rm = TRUE) / length(sim_mult2$rmsea), 
              sum(sim_mult2$rmsea <= 0.08, na.rm = TRUE) / length(sim_mult2$rmsea)),
    rmsea.pvalue = c(sum(sim_mult2$rmsea.pvalue > 0.1, na.rm = TRUE) / length(sim_mult2$rmsea.pvalue), 
                     sum(sim_mult2$rmsea.pvalue > 0.05, na.rm = TRUE) / length(sim_mult2$rmsea.pvalue)),
    srmr = c(sum(sim_mult2$srmr <= 0.05, na.rm = TRUE) / length(sim_mult2$srmr), 
             sum(sim_mult2$srmr <= 0.1, na.rm = TRUE) / length(sim_mult2$srmr)),
    nnfi = c(sum(sim_mult2$nnfi >= 0.97, na.rm = TRUE) / length(sim_mult2$nnfi), 
             sum(sim_mult2$nnfi >= 0.95, na.rm = TRUE) / length(sim_mult2$nnfi)),
    cfi = c(sum(sim_mult2$cfi >= 0.97, na.rm = TRUE) / length(sim_mult2$cfi), 
            sum(sim_mult2$cfi >= 0.95, na.rm = TRUE) / length(sim_mult2$cfi)),
    effect = c(mean(sim_mult2$effectall),
               mean(sim_mult2$effectall)),
    good = sum(sim_mult$pass == "Good", na.rm = TRUE) / length(sim_mult$pass),
    acceptable = (sum(sim_mult$pass == "Acceptable", na.rm = TRUE) +  sum(sim_mult$pass == "Good", na.rm = TRUE)) / length(sim_mult$pass),
    change_fid = c(mean(sim_mult2$change_fid), mean(sim_mult2$change_fid)),
    change_micro = c(mean(sim_mult2$change_micro), mean(sim_mult2$change_micro)), 
    change_sepsis = c(mean(sim_mult2$change_sepsis), mean(sim_mult2$change_sepsis))
  )
  rownames(fit_mult) <- c("good", "acceptable")
  return(fit_mult)
}

#runs a number of different scenarios that mess with the effect sizes and collates the data
runeffect <- function(func1, func2, reps = 100, size = 52, baseline = 0.2, sepsis_baseline = 0.5, 
                      change_sepsis = 0.01, change_micro = 0.5, change_fid = 0.1){
  fid_vect <- change_fid
  micro_vect <- change_micro
  sepsis_vect <- change_sepsis
 all_runs <- mapply(FUN = mult_sorting_effect, 
                    change_fid = fid_vect, 
                    change_micro = micro_vect,
                    change_sepsis = sepsis_vect,
                    MoreArgs = list(reps = reps, size = size, 
                                    func1 = func1,
                                    func2 = func2,
                                    baseline = baseline,
                                    sepsis_baseline = sepsis_baseline))
 
  all_data <- data.frame()
  for (i in 1:ncol(all_runs)){
    #name <- names(data[i])
    chip_good <- all_runs[2, ][[i]][1]
    chip_acc <- all_runs[2, ][[i]][2]
    rmsea_good <- all_runs[3, ][[i]][1]
    rmsea_acc <- all_runs[3, ][[i]][2]
    srmr_good <- all_runs[5, ][[i]][1]
    srmr_acc <- all_runs[5, ][[i]][2]
    nnfi_good <- all_runs[6, ][[i]][1]
    nnfi_acc <- all_runs[6, ][[i]][2]
    cfi_good <- all_runs[7, ][[i]][1]
    cfi_acc <- all_runs[7, ][[i]][2]
    effect <- all_runs[8, ][[i]][1]
    good <- all_runs[9, ][[i]][1]
    acceptable <- all_runs[10, ][[i]][1]
    change_fid <- all_runs[14, ][[i]][1]
    change_micro <- all_runs[15, ][[i]][1]
    change_sepsis <- all_runs[16, ][[i]][1]
    sample_size <- all_runs[17, ][[i]][1]
    first_data <- data.frame( chip_good = chip_good,
                              chip_acc = chip_acc,
                              rmsea_good = rmsea_good,
                              rmsea_acc = rmsea_acc,
                              srmr_good = srmr_good,
                              srmr_acc = srmr_acc,
                              nnfi_good = nnfi_good,
                              nnfi_acc = nnfi_acc,
                              cfi_good = cfi_good,
                              cfi_acc = cfi_acc,
                              effect = effect,
                              overall_good = good,
                              overall_acceptable = acceptable,
                              change_fid = change_fid,
                              change_micro = change_micro,
                              change_sepsis = change_sepsis,
                              sample_size = sample_size
                             )
    all_data <- rbind(all_data, first_data)                
  }
  all_data2 <- cbind(fid_vect, micro_vect, sepsis_vect, all_data)
  all_data3 <- all_data2 %>%
    pivot_longer(cols = c("chip_good",
                          "chip_acc",
                          "rmsea_good",
                          "rmsea_acc",
                          "srmr_good",
                          "srmr_acc",
                          "nnfi_good",
                          "nnfi_acc",
                          "cfi_good",
                          "cfi_acc",
                          "overall_good",
                          "overall_acceptable"),
                 names_to = "fit_measures",
                 values_to = "prop_passing") %>%
    mutate(effect = effect * -100)
  #separate(prop_passing, c("measure", "goodness_of_fit", sep = "_"))
  return(all_data3)
}

#runs a number of different scenarios that mess with the effect sizes and collates the data
runsample <- function(func1, func2, reps = 100, size = 52, baseline = 0.2, sepsis_baseline = 0.5, 
                      change_sepsis = 0.01, change_micro = 0.5, change_fid = 0.1){
  fid_vect <- change_fid
  micro_vect <- change_micro
  sepsis_vect <- change_sepsis
  size_vect <- size
 all_runs <- mapply(FUN = mult_sorting_effect, 
                    change_fid = fid_vect, 
                    change_micro = micro_vect,
                    change_sepsis = sepsis_vect,
                    size = size_vect,
                    MoreArgs = list(reps = reps,  
                                    func1 = func1,
                                    func2 = func2,
                                    baseline = baseline,
                                    sepsis_baseline = sepsis_baseline))
 
  all_data <- data.frame()
  for (i in 1:ncol(all_runs)){
    #name <- names(data[i])
    chip_good <- all_runs[2, ][[i]][1]
    chip_acc <- all_runs[2, ][[i]][2]
    rmsea_good <- all_runs[3, ][[i]][1]
    rmsea_acc <- all_runs[3, ][[i]][2]
    srmr_good <- all_runs[5, ][[i]][1]
    srmr_acc <- all_runs[5, ][[i]][2]
    nnfi_good <- all_runs[6, ][[i]][1]
    nnfi_acc <- all_runs[6, ][[i]][2]
    cfi_good <- all_runs[7, ][[i]][1]
    cfi_acc <- all_runs[7, ][[i]][2]
    aic_good <- all_runs[8, ][[i]][1]
    aic_acc <- all_runs[8, ][[i]][2]
    gfi_good <- all_runs[9, ][[i]][1]
    gfi_acc <- all_runs[9, ][[i]][2]
    agfi_good <- all_runs[10, ][[i]][1]
    agfi_acc <- all_runs[10, ][[i]][2]
    effect <- all_runs[11, ][[i]][1]
    good <- all_runs[12, ][[i]][1]
    acceptable <- all_runs[13, ][[i]][1]
    change_fid <- all_runs[14, ][[i]][1]
    change_micro <- all_runs[15, ][[i]][1]
    change_sepsis <- all_runs[16, ][[i]][1]
    sample_size <- all_runs[17, ][[i]][1]
    first_data <- data.frame( chip_good = chip_good,
                              chip_acc = chip_acc,
                              rmsea_good = rmsea_good,
                              rmsea_acc = rmsea_acc,
                              srmr_good = srmr_good,
                              srmr_acc = srmr_acc,
                              nnfi_good = nnfi_good,
                              nnfi_acc = nnfi_acc,
                              cfi_good = cfi_good,
                              cfi_acc = cfi_acc,
                              aic_good = aic_good,
                              aic_acc = aic_acc,
                              gfi_good = gfi_good,
                              gfi_acc = gfi_acc,
                              agfi_good = agfi_good,
                              agfi_acc = agfi_acc,
                              effect = effect,
                              overall_good = good,
                              overall_acceptable = acceptable,
                              change_fid = change_fid,
                              change_micro = change_micro,
                              change_sepsis = change_sepsis,
                              sample_size = sample_size
                             )
    all_data <- rbind(all_data, first_data)                
  }
  all_data2 <- cbind(fid_vect, micro_vect, sepsis_vect, all_data)
  all_data3 <- all_data2 %>%
    pivot_longer(cols = c("chip_good",
                          "chip_acc",
                          "rmsea_good",
                          "rmsea_acc",
                          "srmr_good",
                          "srmr_acc",
                          "nnfi_good",
                          "nnfi_acc",
                          "cfi_good",
                          "cfi_acc",
                          "aic_good",
                          "aic_acc",
                          "gfi_good",
                          "gfi_acc",
                          "agfi_good",
                          "agfi_acc",
                          "overall_good",
                          "overall_acceptable"),
                 names_to = "fit_measures",
                 values_to = "prop_passing") %>%
    mutate(effect = effect * -100)
  #separate(prop_passing, c("measure", "goodness_of_fit", sep = "_"))
  return(all_data3)
}

#plots extracted data
plotter <- function(data){
  data <- data %>% 
    mutate(sample_size = as.character(sample_size)) %>%
    filter(fit_measures != "agfi_acc",
           fit_measures != "agfi_good",
           fit_measures != "aic_acc",
           fit_measures != "aic_good",
           fit_measures != "gfi_acc",
           fit_measures != "gfi_good")
  data$sample_size <- factor(data$sample_size, levels = c("208", "78", "52", "39"))
  ggplot(data = data, aes(x = effect, y = prop_passing, colour = sample_size)) +
    geom_line(position = position_jitter(width = 0.05, height = 0.05)) +
    ylim(-0.1, 1.1) +
    xlab("% change in sepsis rates as a result of intervention") +
    ylab("% simulations fitting (either acceptable or good fit)") +
    facet_wrap(~fit_measures, ncol = 2,
                   labeller = labeller(fit_measures = 
                                        c("cfi_acc" = "CFI, acceptable fit",
                                        "cfi_good" = "CFI, good fit",
                                        "chip_acc" = "Chi squared, acceptable fit",
                                        "chip_good" = "Chi square, good fit",
                                        "nnfi_acc" = "NNFI, acceptable fit",
                                        "nnfi_good" = "NNFI, good fit",
                                        "overall_acceptable" = "Overall, acceptable fit",
                                        "overall_good" = "Overall, good fit",
                                        "rmsea_acc" = "RMSEA, acceptable fit",
                                        "rmsea_good" = "RMSEA, good fit",
                                        "srmr_acc" = "SRMR, acceptable fit",
                                        "srmr_good" = "SRMR, good fit"))) +
    scale_color_viridis_d(option = "C", direction = -1,
                          name = "Sample size (weeks)")
}

#plots extracted data
plotter2 <- function(data){
  ggplot(data = data, aes(x = sample_size, y = prop_passing)) +
    geom_point() +
    ylim(-0.1, 1.1) +
    xlab("Sample size") +
    ylab("% simulations fitting (either acceptable or good fit)") +
    facet_wrap(~fit_measures, ncol = 2,
                   labeller = labeller(fit_measures = 
                                        c("cfi_acc" = "CFI, acceptable fit",
                                        "cfi_good" = "CFI, good fit",
                                        "chip_acc" = "Chi squared, acceptable fit",
                                        "chip_good" = "Chi square, good fit",
                                        "nnfi_acc" = "NNFI, acceptable fit",
                                        "nnfi_good" = "NNFI, good fit",
                                        "overall_acceptable" = "Overall, acceptable fit",
                                        "overall_good" = "Overall, good fit",
                                        "rmsea_acc" = "RMSEA, acceptable fit",
                                        "rmsea_good" = "RMSEA, good fit",
                                        "srmr_acc" = "SRMR, acceptable fit",
                                        "srmr_good" = "SRMR, good fit"))) +
    scale_color_viridis_c(option = "C", direction = -1,
                          name = "Sample size (weeks)")
}

#setting some defaults
size = 52; baseline = 0.2; change_fid = 0.1; change_micro = 0.75; change_sepsis = 0.01; sepsis_baseline = 0.5; e1_mult = 1; e2_mult = 1; e3_mult = 1
cot_mult = 1; surf_mult = 1; floor_mult = 1; mat_mult = 1; staff_mult = 1
  
```

## Research questions & methodology for answering them

We are interested in investigating the relationships between IPC interventions, fidelity of behaviours associated with such interventions, microbiology on the ward and sepsis. To examine these relationships we will use structural equation models. As well as this there are specific research questions which we will look at using the following methodology.

 1) Do IPC interventions have an effect on sepsis? If so, which ones? And how much? 
      a) Log binomial regression of IPC interventions on sepsis
 2) Is the cleanliness of specific ward "areas" more closely associated with the risk of sepsis? Is the cleanliness of specific ward "areas" more closely associated with specific IPC interventions? 
      a) Looking at the relationships between these specific areas (eg cot, or maternal hands) and sepsis in structural equation models
      b) Log binomial regression of microbiology on sepsis 
 3) Are measures of IPC fidelity adequate for understanding how well protected babies are from sepsis? 
      a) Using the parsimony fit indices to see whether models including microbiology are any better than models which just look at measures of fidelity
 4) Are there specific fidelity or microbiology thresholds we should be aiming for?
      a) Linear regression of microbiology values on sepsis. Thresholds might be defined in one of two ways:
        i) Either a pre-specified desirable sepsis threshold is decided upon, and the microbiology levels are extrapolated from this. 
        ii) If there is a clear change point in levels of sepsis depending on the levels of microbiology, then it might make sense to use these change points to determine thresholds. For example if microbiology levels above a certain threshold lead to a greater increase in sepsis numbers, then you would aim to keep the microbiology levels below this number. 
      
## Model framework

To investigate these questions we will use a combination of structural equation modelling and traditional regression methods. For the structural equation models the modelling framework relies on the assumed relationships as illustrated in the diagram below. 

```{r relationships, echo = FALSE, warning= FALSE, message = FALSE, fig.cap = "Figure 1. Hypothesised elationships between variables in the model. Figure 1A represents the overall conceptual model. In which the initial layer (Inte1 - Inth3) represents 6 hypothesised interventions, which are split into two domains, environmental interventions and hand hygiene interventions. These all have effects on the next layer, which represents the fidelity of these interventions in 5 different sub-domains (Fc = fidelity for cots, Ff = fidelity for floors, Fs = fidelity for surfaces, Fst = fidelity for staff hand hygiene, Fm = fidelity for maternal hand hygiene). Environmental interventions only have effects on environmental fidelity and the same for hand hygiene interventions. The next layer represents the microbiology in each of the 5 different sub-domains (Mc = fidelity for cots, Mf = fidelity for floors, Ms = fidelity for surfaces, Mst = fidelity for staff hand hygiene, Mm = fidelity for maternal hand hygiene). Fidelity in one sub-domain only has an effect on the microbiology of the same sub-domain. All microbiology sub-domains have an effect on sepsis. Figure 1B represents the model that is the focus of the simulations below. Due to sample size problems we simplified the models by focussing on each of the domains in turn ie. environmental hygiene and then hand hygiene. This will be reflected in the eventual analysis. However for the simulations we will only look at the environmental domain, as the hand hygiene domain is a simplification of the environmental domain." }

#first creating the coordinates
coord_dag <- list(
  x = c(Inte1 = 0, 
        Inte2 = 1, 
        Inte3 = 2, 
        Inth1 = 4,
        Inth2 = 5, 
        Inth3 = 6,
        Fc = 0,
        Ff = 1,
        Fs = 2,
        Fst = 4.5,
        Fm = 5.5,
        Mc = 0,
        Mf = 1,
        Ms = 2,
        Mst = 4.5,
        Mm = 5.5,
        S = 3),
  y = c(Inte1 = 5, 
        Inte2 = 5, 
        Inte3 = 5, 
        Inth1 = 5,
        Inth2 = 5, 
        Inth3 = 5,
        Fc = 3,
        Ff = 3,
        Fs = 3,
        Fst = 3,
        Fm = 3,
        Mc = 1,
        Mf = 1,
        Ms = 1,
        Mst = 1,
        Mm = 1,
        S = -1)
)

#next creating the dag
sem_dag <- ggdag::dagify(Fc ~ Inte1,
                         Fc ~ Inte2,
                         Fc ~ Inte3,
                         Ff ~ Inte1,
                         Ff ~ Inte2,
                         Ff ~ Inte3,
                         Fs ~ Inte1,
                         Fs ~ Inte2,
                         Fs ~ Inte3,
                         Fst ~ Inth1,
                         Fst ~ Inth2,
                         Fst ~ Inth3,
                         Fm ~ Inth1,
                         Fm ~ Inth2,
                         Fm ~ Inth3,
                         Mc ~ Fc,
                         Mf ~ Ff,
                         Ms ~ Fs,
                         Mst ~ Fst,
                         Mm ~ Fm,
                         S ~ Mc,
                         S ~ Mf,
                         S ~ Ms,
                         S ~ Mst,
                         S ~ Mm,
                         coords = coord_dag)

#now plotting the dag
ggdag::ggdag(sem_dag) +
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank())



#first creating the coordinates
coord_dag2 <- list(
  x = c(Inte1 = 0, 
        Inte2 = 1, 
        Inte3 = 2, 
        Fc = 0,
        Ff = 1,
        Fs = 2,
        Mc = 0,
        Mf = 1,
        Ms = 2,
        Mst = 4.5,
        Mm = 5.5,
        S = 3),
  y = c(Inte1 = 5, 
        Inte2 = 5, 
        Inte3 = 5, 
        Inth1 = 5,
        Inth2 = 5, 
        Inth3 = 5,
        Fc = 3,
        Ff = 3,
        Fs = 3,
        Fst = 3,
        Fm = 3,
        Mc = 1,
        Mf = 1,
        Ms = 1,
        Mst = 1,
        Mm = 1,
        S = -1)
)

#next creating the dag
sem_dag2 <- ggdag::dagify(Fc ~ Inte1,
                         Fc ~ Inte2,
                         Fc ~ Inte3,
                         Ff ~ Inte1,
                         Ff ~ Inte2,
                         Ff ~ Inte3,
                         Fs ~ Inte1,
                         Fs ~ Inte2,
                         Fs ~ Inte3,
                         Mc ~ Fc,
                         Mf ~ Ff,
                         Ms ~ Fs,
                         S ~ Mc,
                         S ~ Mf,
                         S ~ Ms,
                         S ~ Mst,
                         S ~ Mm,
                         coords = coord_dag)

#now plotting the dag
ggdag::ggdag(sem_dag2) +
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank())
 
```

     
## Decision rules for accepting models

There are a number of different fit metrics used with SEMs, and different people use different thresholds, which means that there is a potential danger of selecting the fit metrics that make the model look best. To ensure that this is not possible, we will determine in advance which fit metrics we will use and what the thresholds for accepting model fit will be. I have chosen the following fit metrics and thresholds such that they will accurately pick up acceptable and well fitting models but not be too restrictive. 

I will look at the following fit metrics to determine whether the models have good or acceptable fit for the data. 

Good fit: 
 
	Chi squared p value  0.05
	AND
	RMSEA  0.05 AND SRMR  0.1 OR SRMR  0.05 AND RMSEA  0.1
	AND
	CFI  0.97 AND NNFI  0.9 OR NNFI  0.97 AND CFI  0.9

 
Acceptable fit:

	Chi squared p value  0.01
	AND
	RMSEA  0.08 AND SRMR  0.1 OR SRMR  0.08 AND RMSEA  0.1
	AND
	CFI  0.95 AND NNFI  0.9 OR NNFI  0.95 AND CFI  0.9

## How the relationships between the data are simulated

There are 3 layers of effect. Each of these is simulated based on the one before. 

1) IPC interventions on fidelity

The effect of IPC interventions on fidelity were simulated using an $rbeta$ distribution. 

The mean of the $rbeta$ distribution for any given values of $\alpha_{fid}$ and $\beta_{fid}$ (where $_{fid}$ represents that the parameters are referring to the effect of interventions on fidelity) is calculated by:

$$E[X_{fid}] = \frac{\alpha_{fid}}{\alpha_{fid} + \beta_{fid}}$$

$\alpha$ is a vector of numbers, calculated by the following equation. 

$$ \alpha_i = 10(C_{fid}(k_1int_{1i} + k_2int_{2i} + k_3int_{3i}) + B_{fid})  $$
Where $C_{fid}$ represents the expected change in fidelity from changing all intervention from the 0 to 1 state (the magnitude of effect of the interventions) and $B_{fid}$ represents the pre-specified baseline fidelity. $int_{xi}$ represent vectors representing whether each interventions is in the on or off state. $k_x$ represents a constant used to scale the effects of individual interventions for the simulations. $\beta_{fid}$ is calculated as $10 - \alpha_{fid}$. 

2) Fidelity on microbiology

The effect of changes in fidelity on microbiology is simulated as a $multivariate \hspace{0.2cm}normal$ distribution with the following parameters describing the means of the distribution. The equation below is repeated for each microbiological "area". The value for each area is then calculated using the $multivariate \hspace{0.2cm}normal$ distribution.

$$E[X_{mic}] = \alpha_{mic} -\beta_{mic}f_{mic} $$
$\alpha_{mic}$ represents the maximum value for the microbiology, and is set at 15, which is the approximate value for the highest $log(m)$ values that we are likely to find. The effect of changes in fidelity ($f_{mic}$) can be altered by changing the value of $\beta_{mic}$. The variance/covariance matrix $(\sigma)$ is set so that the diagonals are  1 and the off-diagonals are 0.5. 

3) Microbiology on sepsis

This is also simulated using an $rbeta$ distribution where $\alpha_{sep}$ and $\beta_{sep}$ are defined as:

$$\alpha_{sep} = \alpha_0 - (\alpha_0 + \beta_0) \times  \delta $$
$$\beta_{sep} = \beta_0 + (\alpha_0 + \beta_0) \times \delta $$
Where $\delta = C_{sep} \times D_{mic}$, $\alpha_0 = B_{sep} \times 100$ and $\beta_0 = 100 - \alpha_0 $. 

$D_{mic}$ is a vector represented by $max_{mic} - micro_i$ where $micro_i$ is a vector of all microbiology values for every area combined by addition and $max_{mic}$ is the largest value of $micro_i$. $C_{sep}$ represents the desired change in the proportion of neonates with sepsis from a 1 log drop in all microbiology parameters, and $B_{sep}$ represents the pre-specified baseline level of sepsis. 

## Plotting this simulation as a time series

```{r time series, echo = FALSE, warning = FALSE, fig.cap = "Figure 2. This time series is plotted by choosing the median and IQR of 1000 simulations using the midpoints of the parameters tested below. The blue line represents microbiology, the red line represents sepsis and the black line represents fidelity of the intervention. Vertical ablines represent the start of various modelled interventions."}

sim_timeseries(reps = 1000, func = sim_enveffect)

```
This time series above represents the average modelled time series, with the timings of all interventions marked on the time series, as well as the effects on fidelity, microbiology and sepsis. It shows the approximate effects of each component of the model on each other and how they relate. 


## How does altering the effect size of different layers alter the probability of accepting the model? 

```{r effect size, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Figure 3. The effects of altering the magnitude of effect of each of the modelled relationships on the proportion of simulations that are accepted. The effect of changing intervention on fidelity (y axis) represents the % change in fidelity based on switching a single intervention from off to on. The effect of changing fidelity on microbiology (x axis) represents the log drop in microbiology based on a 10% increase in fidelity in a single area. The effect of changing microbiology on sepsis (facets) represents the % change in sepsis based on a 1 log drop in all areas of microbiology.The colour of the tiles represents the proportion of simulations that are accepted in each of the situations."}
#simulating data ----
#this function runs the simulator for different parameters
data_effects <- runeffect(func1 = sem_env, func2 = sim_enveffect,
                          change_fid = c(rep(0.05, 9), rep(0.10, 9), rep(0.15, 9)),
                          change_micro = rep(c(0.25, 0.25, 0.25, 0.5, 0.5, 0.5, 0.75, 0.75, 0.75), 3),
                          change_sepsis = rep(c(0.005, 0.01, 0.015), 9),
                          reps = 10,
                          size = 52, 
                          baseline = 0.2,
                          sepsis_baseline = 0.5)

#editing the data a little
effects <- data_effects %>%
  filter(fit_measures == "overall_good") %>%
  mutate(change_micro = as.character(change_micro)) %>%
  mutate(change_fid = 100 * change_fid,
         change_sepsis = change_sepsis)
#editing the data
effects_acc <- data_effects %>%
  filter(fit_measures == "overall_acceptable") %>%
  mutate(change_micro = as.character(change_micro))

#plots a heatmap of the different scenarios
ggplot(data = effects, aes(x = change_micro, y = change_fid, fill = prop_passing)) +
  geom_tile() +
  facet_grid( ~ change_sepsis) +
  scale_fill_viridis_c(option = "C",
                       name = "Proportion of simulations accepted") +
  ylab("Effect of changing intervention on fidelity") +
  xlab("Effect of changing fidelity on microbiology")
```


With increasing magnitude of effect at each of the levels, there are an increasing proportion of simulations that are accepted, which is what would be expected. With all magnitudes of effect at maximum the proportion of simulations that is accepted is `r effects[length(effects$prop_passing),] %>% pull(prop_passing)` whilst with all magnitudes of effect at minimum the proportion of simulations that is accepted is `r effects[1,] %>% pull(prop_passing)`.

## Testing different lengths of study 

```{r sample size, echo = FALSE, warning = FALSE, message = FALSE, eval = FALSE, fig.cap = "Figure 4. A graph showing the proportion of different fit metrics passing at different sample and effect sizes. Facetrs represent the different fit metrics, the x axis represents the different effect sizes and the y axis represents the proportion of simulations with good or acceptable fit. The colours of the lines represent the number of weeks the study will continue for (sample size)." }
#simulating data ----
#this function runs the simulator for different parameters - including years
data_sample <- runsample(func1 = sem_env, func2 = sim_enveffect,
                          change_fid = c(rep(0.05, 4), rep(0.10, 4), rep(0.15, 4)),
                          change_micro = c(rep(0.25, 4), rep(0.5, 4), rep(0.75, 4)),
                          change_sepsis = c(rep(0.005, 4), rep(0.01, 4), rep(0.015, 4)),
                          size = rep(c(39, 52, 78, 208), 3),
                          reps = 100,
                          baseline = 0.2,
                          sepsis_baseline = 0.5)

plotter(data_sample)

```
The proportion of simulations that are accepted depends on the overall effect size as well as the number of weeks for which the study is conducted (sample size).The proportion of simulations that are accepted will act as an indicator of the power of the modelling framework at different effect and sample sizes. We would use a threshold of 80% power as this is standard. If 39 weeks of data (9 months) are collected very few simulations are accepted. At 208 weeks (4 years) almost all of the simulations are accepted, regardless of the effect size. At 52 weeks (1 year) with an approx 5% effect size of each intervention on sepsis, 
`r data_sample %>% filter(sample_size == 52, fit_measures == "overall_good", fid_vect == 0.05, micro_vect == 0.25, sepsis_vect == 0.005) %>% pull(prop_passing)`
% of simulations are accepted as good fit, and 
`r data_sample %>% filter(sample_size == 52, fit_measures == "overall_acceptable", fid_vect == 0.05, micro_vect == 0.25, sepsis_vect == 0.005) %>% pull(prop_passing)`
% of simulations are accepted as acceptable fit. At a moderate effect size of approximately 15%, 
`r data_sample %>% filter(sample_size == 52, fit_measures == "overall_good", fid_vect == 0.1, micro_vect == 0.5, sepsis_vect == 0.010) %>% pull(prop_passing)`
% of simulations are accepted as good fit and 
`r data_sample %>% filter(sample_size == 52, fit_measures == "overall_acceptable", fid_vect == 0.1, micro_vect == 0.5, sepsis_vect == 0.010) %>% pull(prop_passing)`
% are accepted as acceptable, whilst at a large effect size, 
`r data_sample %>% filter(sample_size == 52, fit_measures == "overall_good", fid_vect == 0.15, micro_vect == 0.75, sepsis_vect == 0.015) %>% pull(prop_passing)`
% of simulations are accepted as good fit and 
`r data_sample %>% filter(sample_size == 52, fit_measures == "overall_acceptable", fid_vect == 0.15, micro_vect == 0.75, sepsis_vect == 0.015) %>% pull(prop_passing)`
% are accepted as acceptable fit. With 78 weeks (18 months) of data collection at a low effect size 
`r data_sample %>% filter(sample_size == 78, fit_measures == "overall_good", fid_vect == 0.05, micro_vect == 0.25, sepsis_vect == 0.005) %>% pull(prop_passing)`
% of simulations are accepted as good fit and 
`r data_sample %>% filter(sample_size == 78, fit_measures == "overall_acceptable", fid_vect == 0.05, micro_vect == 0.25, sepsis_vect == 0.005) %>% pull(prop_passing)`
% of simulations are accepted as acceptable fit. At a moderate effect size 
`r data_sample %>% filter(sample_size == 78, fit_measures == "overall_good", fid_vect == 0.1, micro_vect == 0.5, sepsis_vect == 0.010) %>% pull(prop_passing)`
% of simulations are accepted as good fit and 
`r data_sample %>% filter(sample_size == 78, fit_measures == "overall_acceptable", fid_vect == 0.1, micro_vect == 0.5, sepsis_vect == 0.010) %>% pull(prop_passing)`
% of simulationsa re accepted as acceptable, whilst at a large effect size 
`r data_sample %>% filter(sample_size == 78, fit_measures == "overall_good", fid_vect == 0.15, micro_vect == 0.75, sepsis_vect == 0.015) %>% pull(prop_passing)`
% of simulations are accepted as good fit and 
`r data_sample %>% filter(sample_size == 78, fit_measures == "overall_acceptable", fid_vect == 0.15, micro_vect == 0.75, sepsis_vect == 0.015) %>% pull(prop_passing)`
% are accepted as acceptable fit. 

Due to time and resource constraints we cannot continue the study for an unlimited time, so continuing for 208 weeks (2 years) is not possible. Also, very small effect sizes may not be clinically relevant. Therefore, we would like to continue the study up to 78 weeks (18 months) to enable us adequate power to detect any effect larger than a small one. 


### Question 1: Do IPC interventions have an effect on sepsis? If so which ones? And how much? 

We will fit an SEM model as illustrated above. However, alongside this we will also perform a log binomial regression of different IPC measures against sepsis. This will give us the risk ratio between these measures and the risk of sepsis.

```{r question 1, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Table 1. A table showing the results of coefficients of a log binomial model of the different IPC interventions on sepsis. The rows represent situations where the effect of certain interventions has been nullified. ie a situation where one of the interventions has no effect on sepsis. The columns represent the different interventions."}
#simulating with different scenarios
#one in which all interventions have an effect
allhaveeffect <- logbin_ipcsepsis(func = sim_envindiv, e1_mult = 1, e2_mult = 1, e3_mult = 1, reps = 100)
#one in which the first intervention has no effect
int1missing <- logbin_ipcsepsis(func = sim_envindiv, e1_mult = 0, e2_mult = 1, e3_mult = 1, reps = 100)
#one in which the second intervention has no effect
int2missing <- logbin_ipcsepsis(func = sim_envindiv, e1_mult = 1, e2_mult = 0, e3_mult = 1, reps = 100)
#one in which the third intervention has no effect
int3missing <- logbin_ipcsepsis(func = sim_envindiv, e1_mult = 1, e2_mult = 1, e3_mult = 0, reps = 100)

altogether <- as.data.frame(rbind(allhaveeffect, int1missing, int2missing, int3missing))
altogether <- add_column(altogether, Effects = c("All ints have effect", "Int1 missing", "Int2 missing", "Int3 missing"), .before = "int_e1")
gt(altogether)

```

In all situations the model converges well. From the table it looks like the model is good at picking up whether specific interventions have an effect on sepsis. The risk ratio is between 0.89 and 0.94 for the interventions that do have an effect. When interventions don't have an effect the risk ratio is between 

### Question 2: Is the cleanliness of specific ward "areas" more closely associated with the risk of sepsis? Is the cleanliness of specific ward "areas" more closely associated with specific IPC interventions? 

Looking at whether the cleanliness of specific ward "areas" are most closely associated with the risk of sepsis would allow us to determine which areas are most useful for intervention. If specific ward areas are most associated with sepsis and it is clear which interventions affect these primarily, then these areas can be targeted with interventions that are most likely to be effective.

This will be done by looking at the specific relationships between different microbiology areas and sepsis using the SEM as above. We will also perform log binomial regression of microbiology on sepsis.

To determine how well the model will be at identifying individual ward areas as responsible for decreases in sepsis I will look at the coefficients of the variables in the model. 

```{r question 2, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Table 2. A table showing the coefficients of the log binomial model of the microbiology results from different ward areas on the risk of sepsis. The rows represent different situations where specific areas have been changed to have no effect on sepsis. The columns represent the different specific areas."}

#need to spend some time thinking about how to do this bit - it's not immediately obvious how to alter the effects of the different areas
allmicroeffect <- logbin_microsepsis(func = sim_envindiv, cot_mult = 1, floor_mult = 1, surf_mult = 1, staff_mult = 1, mat_mult = 1, reps = 100)
nocoteffect <- logbin_microsepsis(func = sim_envindiv, cot_mult = 0, floor_mult = 1, surf_mult = 1, staff_mult = 1, mat_mult = 1, reps = 100)
noflooreffect <- logbin_microsepsis(func = sim_envindiv, cot_mult = 1, floor_mult = 0, surf_mult = 1, staff_mult = 1, mat_mult = 1, reps = 100)

allmicro <- as.data.frame(rbind(allmicroeffect, nocoteffect, noflooreffect))
allmicro <- add_column(allmicro, Effects = c("All areas have an effect", "Cot has no effect", "Floor has no effect"), .before = "cot")
gt(allmicro)

```

The models converged well. The risk ratio for a 1 unit increase in the microbiological cleanliness of a specific ward area is around 1.02. For the areas which have been artificially changed to have no effect on sepsis in the model, the risk ratio decreases to be closer to 1. 



### Question 3: Are measures of IPC fidelity adequate for understanding how well protected babies are from sepsis?

We will answer this question by creating the following 2 structural equation models and using parsimony fit indices to determine which is the most parsimonious. 

1) An SEM including interventions, fidelity and sepsis;
2) An SEM including interventions, fidelity, microbiology and sepsis.

```{r question 3, echo = FALSE, warning = FALSE, message = FALSE}

#chi square difference test, aic, gfi and agfi - though will use aic as the main one
#cant use chi square difference test as the models are not nested (only used for nested models)
#interventions only needs some work i think there is a problem with the fitting - i think it is related to degrees of freedom potentially
#aic - lower is better
#gfi - higher is better - greater than 0.95 indicates good fit, greater than 0.9 indicates acceptable fit
#agfi - higher is better - greater than 0.9 indicates good fit, greater than 0.85 indicates acceptable fit

run_intfid <- runsample(func1 = sem_env_intfid, func2 = sim_enveffect,
                          change_fid = 0.1,
                          change_micro = 0.5,
                          change_sepsis = 0.01,
                          size = 78,
                          reps = 100,
                          baseline = 0.2,
                          sepsis_baseline = 0.5)

run_intfidmicro <- runsample(func1 = sem_env, func2 = sim_enveffect,
                          change_fid = 0.1,
                          change_micro = 0.5,
                          change_sepsis = 0.01,
                          size = 78,
                          reps = 100,
                          baseline = 0.2,
                          sepsis_baseline = 0.5)

```

The simpler model, excluding microbiology, has a lower AIC and higher AGFI and GFI, indicating better fit than the more complex model. AIC `r run_intfid %>% filter(fit_measures == "aic_good") %>% pull(prop_passing)` vs `r run_intfidmicro %>% filter(fit_measures == "aic_good") %>% pull(prop_passing)`, AGFI `r run_intfid %>% filter(fit_measures == "agfi_good") %>% pull(prop_passing)` vs `r run_intfidmicro %>% filter(fit_measures == "agfi_good") %>% pull(prop_passing)` and GFI `r run_intfid %>% filter(fit_measures == "gfi_good") %>% pull(prop_passing)` vs `r run_intfidmicro %>% filter(fit_measures == "gfi_good") %>% pull(prop_passing)`. 

This might indicate that measures of IPC fidelity are adequate for determining the level of IPC practice on the ward, and that measuring microbiology as well is not helpful. 


### Question 4: Are there specific fidelity or microbiology thresholds we should be aiming for?

This will be done by performing linear regression of microbiology on sepsis. This might be analysed in two different ways depending on whether the relationship is linear. 

If the relationship is linear then the threshold will be based on clinically "acceptable" levels of sepsis on the ward. If the relationship is not linear then it might be clear that there is a threshold below which sepsis becomes a lot less common. If the data looks like it warrants it then change points in the data might be detected, to siee if there are points at which the relationship between microbiology and sepsis changes significantly. 

```{r question 4, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Figure 5. A scatter plot showing the microbiogy results on the x axis and the proportion of neonates with sepsis on the y axis. The points represent data from a single simulation. The grey lines represent the regression slope from 100 individual simulations, and the thick black line represents the average regression line from all 100 simulations"}

lin_microsepsis(func = sim_enveffect, reps = 100)

```

You can see here that we will plot the relationship between microbiology and sepsis.

If the relationship is linear as it appears here then we can make recommendations that to reduce sepsis to level x, microbiology should be reduced to level y. If it is not linear then we will try to determine the point at which you get the most benefit from reducing the microbial load to that level. 


```{r notes, echo = FALSE, message = FALSE}

### Notes
#- Can't have covariance relationship between micro_mat and micro_staff as theses are exogenous variables and lavaan is unable to estimate the covariance relationship between them. Can either leave that relationship out or #use fixed.x = FALSE
# - Think about modelling time dependent decay
#      - Model time dependent decay in the simulations
#      - In the analysis can look at time since intervention - an asymptotic or linear decay function to see how quickly the effects of interventions decay
# - Need to remember that if there is autocorrelation after accounting for the covariates (ie autocorrelation of the residuals), then splines for time trends will need to be added to account for this, as variables are #supposed to be independent conditioning on explanatory variables
 
# The most stringent accepted fit metrics are: 

# - Chi squared p value - >= 0.05 (good), >= 0.01 (acceptable)
# - RMSEA - <= 0.05 (good), <= 0.08 (acceptable)
# - SRMR - <= 0.05 (good), <= 0.1 (acceptable)
# - CFI - >= 0.97 (good), >= 0.95 (acceptable)
# - NNFI - >= 0.97 (good), >= 0.95 (acceptable)
```
